Matching Bullets

### 2015-11-24 imaging-paper.Rnw
Shorten fox news URL so it doesn't overlap

Rough outline:
\begin{enumerate}
\item Description of the problem: Standard operating practice, 2009 NAS report
\item Description of the Results
\item Walkthrough of the process
\item \hh{XXX Alternative approaches: IBIS database and the NRC report against it\footnote{Fox report on the NRC report \url{http://www.foxnews.com/story/2008/03/05/nationwide-firearms-
database-shot-down-by-government-sponsored-study.html}.
NRC report: \url{http://www.nap.edu/catalog/12162/ballistic-imaging}} }
\end{enumerate}

>>>>

Rough outline:
\begin{enumerate}
\item Description of the problem: Standard operating practice, 2009 NAS report
\item Description of the Results
\item Walkthrough of the process
\item \hh{XXX Alternative approaches: IBIS database and the NRC report against it\footnote{Fox report on the NRC report \url{http://goo.gl/XurSVl}.
NRC report: \url{http://www.nap.edu/catalog/12162/ballistic-imaging}} }
\end{enumerate}
